Bouston  Tests

### 2017-07-20 slowtests/slowtests-boston.Rmd
ready for release

## Cubist

# `Cubist` package

@@

## Decision trees

# `rpart` package

@@

# `party` package

@@

# `partykit` package

@@

## Bagging

# `ipred` package

@@

## Random forests

# `randomForest` package

@@

# `ranger` package

@@

## Boosting

# `gbm` package

@@

# `xgboost` package
```{r}
set.seed(101)
boston.xgb <- xgboost::xgboost(
  data = data.matrix(subset(boston, select = -cmedv)), label = boston$cmedv,
  objective = "reg:linear", nrounds = 5000, max_depth = 3, eta = 0.001,
  colsample_bytree = 0.8, subsample = 0.5,
  save_period = NULL, verbose = 0
)
bostonHousingTest(boston.xgb)
```

## Neural networks

# `nnet` package
```{r}
set.seed(101)
boston.nnet <- nnet::nnet(cmedv ~ ., data = boston, size = 6, decay = 0.1,
                          linout = TRUE, trace = FALSE)
bostonHousingTest(boston.nnet)
```

## Support vector machines

# `e1071` package

@@

# `kernlab` package

@@

## Linear/generalized linear models

# `stats` package

@@

## Multivariate adaptive regression splines

# `earth` package

@@

# `mda` package

>>>>

# Cubist

## `Cubist` package

@@

# Decision trees

## `rpart` package

@@

## `party` package

@@

## `partykit` package

@@

# Bagging

## `ipred` package

@@

# Random forests

## `randomForest` package

@@

## `ranger` package

@@

# Boosting

## `gbm` package

@@

## `xgboost` package
```{r}
set.seed(101)
boston.xgb <- xgboost::xgboost(
  data = data.matrix(subset(boston, select = -cmedv)), label = boston$cmedv,
  objective = "reg:linear", nrounds = 5000, max_depth = 3, eta = 0.001,
  colsample_bytree = 0.8, subsample = 0.5,
  save_period = NULL, verbose = 0
)
bostonHousingTest(boston.xgb)
```

# Neural networks

## `nnet` package
```{r}
set.seed(101)
boston.nnet <- nnet::nnet(cmedv ~ ., data = boston, size = 6, decay = 0.1,
                          linout = TRUE, trace = FALSE)
bostonHousingTest(boston.nnet)
```

# Support vector machines

## `e1071` package

@@

## `kernlab` package

@@

# Linear/generalized linear models

## `stats` package

@@

# Multivariate adaptive regression splines

## `earth` package

@@

## `mda` package

### 2017-07-20 slowtests/slowtests-pima.Rmd
ready for release

```{r}
set.seed(101)
pima.gbm <- gbm::gbm(diabetes ~ ., 
                     data = na.omit(pima),
                     distribution = "multinomial",
                     n.trees = 5000,
                     interaction.depth = 3,
                     shrinkage = 0.001,
                     cv.folds = 5,
                     verbose = FALSE)
best.iter <- gbm::gbm.perf(pima.gbm, method = "cv", plot.it = FALSE)
pimaIndiansTest(pima.gbm, n.trees = best.iter)
pimaIndiansTest(pima.gbm, n.trees = best.iter, prob = TRUE)
```

>>>>

```{r}
set.seed(101)
pima.gbm <- gbm::gbm(unclass(diabetes) - 1 ~ ., 
                     data = na.omit(pima),
                     distribution = "bernoulli",
                     n.trees = 5000,
                     interaction.depth = 3,
                     shrinkage = 0.001,
                     # cv.folds = 5,
                     verbose = FALSE)
best.iter <- gbm::gbm.perf(pima.gbm, method = "OOB", plot.it = FALSE)
pimaIndiansTest(pima.gbm, n.trees = best.iter)
pimaIndiansTest(pima.gbm, n.trees = best.iter, prob = TRUE)
```
